Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-07-06 latex/ICPP21/paper.tex
converted to single column format and fixed up some issues

\documentclass[sigconf]{acmart}

@@

\title{Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms}

@@

\begin{figure*}[t!]
%
\subfloat[One thread]{
\centering
\renewcommand{\datafile}{data/matmul_seq.dat}
\renewcommand{\threads}{1}
%\input{plots/matmul_perf}
\includegraphics{tikz-taps/paper-figure2.pdf}
%\caption{Single-threaded matrix multiplication performance}
\label{fig:matmul_seq}}
%
\hfill
\subfloat[Six threads]{
\centering
\renewcommand{\datafile}{data/matmul_par_6.dat}
\renewcommand{\threads}{6}
%\input{plots/matmul_perf}
\includegraphics{tikz-taps/paper-figure3.pdf}
%\caption{Multithreaded matrix multiplication performance (6 threads)}
\label{fig:matmul_par_6}}
%
\hfill
\subfloat[Twelve threads]{
\centering
\renewcommand{\datafile}{data/matmul_par_12.dat}
\renewcommand{\threads}{12}
%\input{plots/matmul_perf}
\includegraphics{tikz-taps/paper-figure4.pdf}
%\caption{Multithreaded matrix multiplication performance (6 threads)}
\label{fig:matmul_par_12}}
%
\caption{Single- and multi-threaded square matrix multiplication performance, relative to $2n^3$ operations.  The machine peak with respect to classical algorithms is given as a dotted line.}
\label{fig:matmul_perf}
\end{figure*}

@@

\begin{figure*}[ht!]
%
\subfloat[Training accuracy]{
\centering
\renewcommand{\datafile}{data/NN_acc.dat}
\renewcommand{\set}{train}
%\input{plots/NN_acc}
\includegraphics{tikz-taps/paper-figure5.pdf}
\label{fig:NN_acc_train}}
%
\hfill
\subfloat[Test accuracy]{
\centering
\renewcommand{\datafile}{data/NN_acc.dat}
\renewcommand{\set}{test}
%\input{plots/NN_acc}
\includegraphics{tikz-taps/paper-figure6.pdf}
\label{fig:NN_acc_test}}
%
\caption{MLP network accuracy for MNIST data set}
\label{fig:NN_acc}
\end{figure*}

\begin{figure}[hb!]
\centering
%\input{figs/neuralnet}
\includegraphics{tikz-taps/paper-figure7.pdf}
\caption{Multi-Layer Perceptron network structure}
\label{fig:neuralnet}
\end{figure}

@@

@@

\begin{figure*}[t!]
%
\subfloat[One thread]{
\centering
\renewcommand{\datafile}{data/NN_seq.dat}
\renewcommand{\threads}{1}
%\input{plots/NN_reltime}
\includegraphics{tikz-taps/paper-figure8.pdf}
\label{fig:NNreltime_seq}}
%
\hfill
\subfloat[Six threads]{
\centering
\renewcommand{\datafile}{data/NN_par_6.dat}
\renewcommand{\threads}{6}
%\input{plots/NN_reltime}
\includegraphics{tikz-taps/paper-figure9.pdf}
\label{fig:NNreltime_par_6}}
%
\hfill
\subfloat[Twelve threads]{
\centering
\renewcommand{\datafile}{data/NN_par_12.dat}
\renewcommand{\threads}{12}
%\input{plots/NN_reltime}
\includegraphics{tikz-taps/paper-figure10.pdf}
\label{fig:NNreltime_par_12}}
%
\caption{Network training time relative to using classical matrix multiplication}
\label{fig:NNreltime}
\end{figure*}

@@

\begin{figure}
%
\subfloat[One thread]{
\centering
%\input{plots/VGG_time_seq}
\includegraphics{tikz-taps/paper-figure11.pdf}
\label{fig:vgg_seq}}%
\hfill	
\subfloat[Six threads]{
\centering
%\input{plots/VGG_time}
\includegraphics{tikz-taps/paper-figure12.pdf}
\label{fig:vgg_par6}}
%
\caption{Per-batch training time on the fully connected layers of VGG-19 using $\dims{4,4,2}$ and Classical}
\label{fig:vgg}
\end{figure}

>>>>

\documentclass[manuscript]{acmart}

@@

\title[Accelerating NN Training using APA Matrix Multiplication Algorithms]{Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms}

@@

\begin{figure*}[t!]
%
\subfloat[One thread]{
\centering
\renewcommand{\datafile}{data/matmul_seq.dat}
\renewcommand{\threads}{1}
%\input{plots/matmul_perf}
\includegraphics[scale=.85]{tikz-taps/paper-figure2.pdf}
%\caption{Single-threaded matrix multiplication performance}
\label{fig:matmul_seq}}
%
\hfill
\subfloat[Six threads]{
\centering
\renewcommand{\datafile}{data/matmul_par_6.dat}
\renewcommand{\threads}{6}
%\input{plots/matmul_perf}
\includegraphics[scale=.85]{tikz-taps/paper-figure3.pdf}
%\caption{Multithreaded matrix multiplication performance (6 threads)}
\label{fig:matmul_par_6}}
%
\hfill
\subfloat[Twelve threads]{
\centering
\renewcommand{\datafile}{data/matmul_par_12.dat}
\renewcommand{\threads}{12}
%\input{plots/matmul_perf}
\includegraphics[scale=.85]{tikz-taps/paper-figure4.pdf}
%\caption{Multithreaded matrix multiplication performance (6 threads)}
\label{fig:matmul_par_12}}
%
\caption{Single- and multi-threaded square matrix multiplication performance, relative to $2n^3$ operations.  The machine peak with respect to classical algorithms is given as a dotted line.}
\label{fig:matmul_perf}
\end{figure*}

@@

\begin{figure*}[ht!]
%
\subfloat[Training accuracy]{
\centering
\renewcommand{\datafile}{data/NN_acc.dat}
\renewcommand{\set}{train}
%\input{plots/NN_acc}
\includegraphics[scale=.9]{tikz-taps/paper-figure5.pdf}
\label{fig:NN_acc_train}}
%
\hfill
\subfloat[Test accuracy]{
\centering
\renewcommand{\datafile}{data/NN_acc.dat}
\renewcommand{\set}{test}
%\input{plots/NN_acc}
\includegraphics[scale=.9]{tikz-taps/paper-figure6.pdf}
\label{fig:NN_acc_test}}
%
\caption{MLP network accuracy for MNIST data set}
\label{fig:NN_acc}
\end{figure*}

@@

\begin{figure}[ht!]
\centering
%\input{figs/neuralnet}
\includegraphics{tikz-taps/paper-figure7.pdf}
\caption{Multi-Layer Perceptron network structure}
\label{fig:neuralnet}
\end{figure}

@@

\begin{figure*}[t!]
%
\subfloat[One thread]{
\centering
\renewcommand{\datafile}{data/NN_seq.dat}
\renewcommand{\threads}{1}
%\input{plots/NN_reltime}
\includegraphics[scale=.85]{tikz-taps/paper-figure8.pdf}
\label{fig:NNreltime_seq}}
%
\hfill
\subfloat[Six threads]{
\centering
\renewcommand{\datafile}{data/NN_par_6.dat}
\renewcommand{\threads}{6}
%\input{plots/NN_reltime}
\includegraphics[scale=.85]{tikz-taps/paper-figure9.pdf}
\label{fig:NNreltime_par_6}}
%
\hfill
\subfloat[Twelve threads]{
\centering
\renewcommand{\datafile}{data/NN_par_12.dat}
\renewcommand{\threads}{12}
%\input{plots/NN_reltime}
\includegraphics[scale=.85]{tikz-taps/paper-figure10.pdf}
\label{fig:NNreltime_par_12}}
%
\caption{Network training time relative to using classical matrix multiplication}
\label{fig:NNreltime}
\end{figure*}

@@

\begin{figure}
%
\subfloat[One thread]{
\centering
%\input{plots/VGG_time_seq}
\includegraphics[scale=1.75]{tikz-taps/paper-figure11.pdf}
\label{fig:vgg_seq}}%
\hfill	
\subfloat[Six threads]{
\centering
%\input{plots/VGG_time}
\includegraphics[scale=1.75]{tikz-taps/paper-figure12.pdf}
\label{fig:vgg_par6}}
%
\caption{Per-batch training time on the fully connected layers of VGG-19 using $\dims{4,4,2}$ and Classical}
\label{fig:vgg}
\end{figure}
